
Exploratory data analysis for FIRE-mouse split-seq project

## Load split-pipe data into Seurat

```{r eval=FALSE}

# in bash terminal:
# conda activate spatial

library(Seurat)
library(tidyverse)
library(cowplot)
library(Matrix)
library(viridis)
library(presto)
library(harmony)
theme_set(theme_cowplot())

setwd("/dfs3b/swaruplab/smorabit/analysis/FIRE_mouse_2021/")

# directories
splitpipe_outdir <- "~/swaruplab/smorabit/data/FIRE_mouse_2021/analysis/EDA/"
data_dir <- "data/"
fig_dir <- 'figures/'


umap_theme <- theme(
  axis.line=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks=element_blank(),
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  panel.background=element_blank(),
  panel.border=element_blank(),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  plot.background=element_blank()
)

# re-load data:
seurat_obj <- readRDS(paste0(data_dir, 'FIRE_mouse_seurat.rds'))


################################################################################
# Load split-pipe data into Seurat
################################################################################

sublibraries <- paste0(splitpipe_outdir, dir(splitpipe_outdir), '/')

seurat_list <- list()
for(sublibrary in dir(splitpipe_outdir)){
  print(sublibrary)
  lib <- paste0(splitpipe_outdir, sublibrary, '/')

  # load data from split-pipe
  X <- Matrix::readMM(paste0(lib, 'all-well/DGE_filtered/DGE.mtx')) %>% t
  genes <- read.csv(paste0(lib, 'all-well/DGE_filtered/genes.csv'))
  lib_meta <- read.csv(paste0(lib, 'all-well/DGE_filtered/cell_metadata.csv'))
  rownames(lib_meta) <- lib_meta$cell_barcode

  # set row and col names for expression matrix X:
  colnames(X) <- lib_meta$cell_barcode
  rownames(X) <- genes$gene_name

  # create seurat object
  cur <- Seurat::CreateSeuratObject(
    counts = X,
    meta = lib_meta
  )
  cur$sublibrary <- sublibrary
  seurat_list[[sublibrary]] <- cur
}

# merge seurat objects:
seurat_obj <- merge(seurat_list[[1]], seurat_list[2:length(seurat_list)])
rm(seurat_list); gc();

# add sample metadata:
sample_meta <- read.csv('~/swaruplab/smorabit/analysis/FIRE_mouse_2021/data/splitseq_meta.csv')
seurat_obj@meta.data <- cbind(seurat_obj@meta.data, sample_meta[match(as.character(seurat_obj$sample), as.character(sample_meta$SampleID)),])
all.equal(as.character(seurat_obj$sample), as.character(seurat_obj$SampleID))


```

Quality Control:

```{r eval=FALSE}

seurat_obj[["percent.mt"]] <- PercentageFeatureSet(object = seurat_obj, pattern = "^mt-")
pdf(paste0(fig_dir, "qc_violin_plot.pdf"), width=10, height=10)
VlnPlot(seurat_obj, group.by="SampleID", features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 1, pt.size=0)
dev.off()

filter <- !(seurat_obj$nCount_RNA > 100000 | seurat_obj$percent.mt > 6 | seurat_obj$nFeature_RNA > 12000)

seurat_obj <- seurat_obj[,filter]

```

Processing

```{r eval=FALSE}

# normalization
seurat_obj <- NormalizeData(seurat_obj)
seurat_obj <- ScaleData(seurat_obj, features=rownames(seurat_obj))
seurat_obj <- FindVariableFeatures(seurat_obj, nfeatures=3500)

# remove any mito genes from variable feature set:
VariableFeatures(seurat_obj) <- VariableFeatures(seurat_obj)[!grepl("^mt-", VariableFeatures(seurat_obj))]

# dim reduction
seurat_obj <- RunPCA(seurat_obj, features=VariableFeatures(seurat_obj))
seurat_obj <- RunUMAP(seurat_obj, dims = 1:30)

# clustering
# too many cells to use Leiden clustering unfortunately
# https://github.com/satijalab/seurat/issues/2294
seurat_obj <- FindNeighbors(seurat_obj)
seurat_obj <- FindClusters(seurat_obj, resolution = 0.75)

# save processed seurat obj
# saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat_noQC.rds'))


```

Visualization:

```{r eval=FALSE}

################################################################################
# categorical variables
################################################################################

# UMAP + Clusters
p <- DimPlot(seurat_obj, label=TRUE) + umap_theme
pdf(paste0(fig_dir, 'umap_clusters.pdf'), width=8, height=7)
p
dev.off()

# color by sample
p <- DimPlot(seurat_obj, group.by='SampleID') + umap_theme
pdf(paste0(fig_dir, 'umap_samples.pdf'), width=10, height=7)
p
dev.off()

# highlight high percent.mt
seurat_obj$high.mt <- seurat_obj$percent.mt > 5
p <- DimPlot(seurat_obj, cells.highlight=colnames(seurat_obj)[seurat_obj$high.mt]) +
  umap_theme + theme(legend.position='bottom') + ggtitle('% MT reads > 5')
pdf(paste0(fig_dir, 'umap_high_mt.pdf'), width=6, height=6)
p
dev.off()

# split by DX color by sample
p <- DimPlot(seurat_obj, split.by='DX', group.by='SampleID', ncol=3) + umap_theme
pdf(paste0(fig_dir, 'umap_sample_splitby_DX.pdf'), width=10, height=6)
p
dev.off()

# split by DX:
p <- DimPlot(seurat_obj, split.by='DX', group.by='DX', ncol=3) + umap_theme
pdf(paste0(fig_dir, 'umap_DX_split.pdf'), width=8, height=6)
p
dev.off()

# split by Sublibrary:
p <- DimPlot(seurat_obj, split.by='sublibrary', group.by='sublibrary', ncol=4) + umap_theme
pdf(paste0(fig_dir, 'umap_sublibrary_split.pdf'), width=12, height=6)
p
dev.off()

################################################################################
# quality control featureplots
################################################################################
p <- FeaturePlot(seurat_obj,features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, max.cutoff='q99', order=TRUE)

pdf(paste0(fig_dir, 'featureplot_qc.pdf'), width=14, height=4, useDingbats=FALSE)
p
dev.off()

#################################################################################
# marker genes
################################################################################

markers <- c('Csf1r', 'Aqp4', 'Mobp', 'Pdgfra', 'Slc17a7', 'Gad2')
pdf(paste0(fig_dir, 'featureplot_markers.pdf'), width=5, height=5, useDingbats=FALSE)

for(gene in markers){
  print(gene)
  p1 <- FeaturePlot(seurat_obj, features=gene, max.cutoff='q99', order=TRUE) +
    scale_color_gradientn(colors=viridis(256), guide = guide_colorbar(barwidth=15, barheight=0.5, ticks=FALSE)) +
    umap_theme + theme(legend.position='bottom')

  print(p1)
}
dev.off()

```

Align samples using Harmony:

```{r eval=FALSE}

library(harmony)

# harmony + umap:
seurat_obj <- RunHarmony(seurat_obj, dims=1:20, group.by='SampleID')
seurat_obj <- RunUMAP(seurat_obj, reduction='harmony', dims = 1:20, n.neighbors=15L, min.dist=0.10)
# seurat_obj <- RunTSNE(seurat_obj, reduction='harmony', dims = 1:30)

seurat_obj <- FindNeighbors(seurat_obj, dims=1:20, reduction='harmony', annoy.metric='cosine')
seurat_obj <- FindClusters(seurat_obj, resolution = 0.7)

```

Save processed seurat obj and format for scanpy:
```{r eval=FALSE}
library(SeuratDisk)

# save as .rds
saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat.rds'))

# save individual pieces of seurat object to load into python:

# save data matrix:
X <- GetAssayData(seurat_obj, assay='RNA', slot='data')
Matrix::writeMM(X, file=paste0(data_dir, 'FIRE_mouse_normCounts.mtx'))

# save gene names:
write.table(
  data.frame('gene'=rownames(X)),
  file=paste0(data_dir, 'gene_names.csv'),
  quote=F,
  row.names=F,
  col.names=F
)

# save harmony matrix as csv
write.csv(seurat_obj@reductions$harmony@cell.embeddings, file=, paste0(data_dir, 'FIRE_mouse_harmony.csv'), quote=F, row.names=F)

# save metadata:
meta <- seurat_obj@meta.data
meta$barcode <- colnames(seurat_obj)
meta$UMAP1 <- seurat_obj@reductions$umap@cell.embeddings[,1]
meta$UMAP2 <- seurat_obj@reductions$umap@cell.embeddings[,2]

write.csv(meta, file=paste0(data_dir, 'FIRE_mouse_meta.csv'), quote=F, row.names=F)


```

Transfer scanpy data over to Seurat obj:
```{r eval=FALSE}

scanpy_meta <- read.csv(paste0(data_dir,'scanpy_meta.csv'))
seurat_obj$leiden_res0.7 <- factor(scanpy_meta$leiden_res0.7, levels=min(scanpy_meta$leiden_res0.7):max(scanpy_meta$leiden_res0.7))
seurat_obj$leiden_res1.5 <- factor(scanpy_meta$leiden_res1.5, levels=min(scanpy_meta$leiden_res1.5):max(scanpy_meta$leiden_res1.5))
Idents(seurat_obj) <- seurat_obj$leiden_res1.5

paga_umap <- as.matrix(select(scanpy_meta, c(paga_UMAP1, paga_UMAP2)))
rownames(paga_umap) <- colnames(seurat_obj)
seurat_obj@reductions$paga_umap <-  CreateDimReducObject(
    embeddings=paga_umap,
    key="umap_",
    assay="RNA"
)

```

Visualization

```{r eval=FALSE}

# UMAP + Clusters
p <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap') + umap_theme
pdf(paste0(fig_dir, 'umap_clusters.pdf'), width=8, height=7)
p
dev.off()

p1 <- DimPlot(seurat_obj,  group.by='leiden_res0.7', label=TRUE, reduction='paga_umap') +
 umap_theme + NoLegend() + ggtitle('Leiden clusters, resolution = 0.7')
p2 <- DimPlot(seurat_obj, group.by='leiden_res1.5', label=TRUE, reduction='paga_umap') +
  umap_theme + NoLegend() + ggtitle('Leiden clusters, resolution = 1.5')

pdf(paste0(fig_dir, 'umap_clusters_compareRes.pdf'), width=12, height=6)
p1 | p2
dev.off()

# color by sample
p <- DimPlot(seurat_obj, group.by='SampleID', reduction='paga_umap') + umap_theme
pdf(paste0(fig_dir, 'umap_samples.pdf'), width=10, height=7)
p
dev.off()

# split by DX color by sample
p <- DimPlot(seurat_obj, split.by='DX', group.by='SampleID', ncol=3, reduction='paga_umap') + umap_theme
pdf(paste0(fig_dir, 'umap_sample_splitby_DX.pdf'), width=10, height=6)
p
dev.off()

# split by DX:
p <- DimPlot(seurat_obj, split.by='DX', group.by='DX', ncol=3,reduction='paga_umap') + umap_theme
pdf(paste0(fig_dir, 'umap_DX_split.pdf'), width=8, height=6)
p
dev.off()

# split by Sublibrary:
p <- DimPlot(seurat_obj, split.by='sublibrary', group.by='sublibrary', ncol=4, reduction='paga_umap') + umap_theme
pdf(paste0(fig_dir, 'umap_sublibrary_split.pdf'), width=12, height=6)
p
dev.off()

#################################################################################
# marker genes
################################################################################

markers <- c('Csf1r', 'Aqp4', 'Mobp', 'Pdgfra', 'Slc17a7', 'Gad2')
pdf(paste0(fig_dir, 'featureplot_markers.pdf'), width=5, height=5, useDingbats=FALSE)

for(gene in markers){
  print(gene)
  p1 <- FeaturePlot(seurat_obj, features=gene, max.cutoff='q99', order=TRUE, reduction='paga_umap') +
    scale_color_gradientn(colors=viridis(256), guide = guide_colorbar(barwidth=15, barheight=0.5, ticks=FALSE)) +
    umap_theme + theme(legend.position='bottom')

  print(p1)
}
dev.off()


markers <- c('Csf1r', 'Cx3cr1', 'Cd163', 'Tnc', 'Gfap', 'Aqp4', 'Mobp', 'Mog', 'Pdgfra', 'Slc17a7', 'Rorb', 'Themis', 'Nrgn', 'Gad2', 'Vip', 'Pvalb', 'Sst', 'Lamp5')
p <- DotPlot(seurat_obj, features=markers) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256)))
pdf(paste0(fig_dir, 'dotplot_markers.pdf'), width=12, height=6, useDingbats=FALSE)
p
dev.off()

# plot MG in each condition
mg_genes <- c('Csf1r')
p <- VlnPlot(subset(seurat_obj, seurat_clusters==20), features=mg_genes, group.by='DX', pt.size=0.1, ncol=1) + xlab('') + NoLegend()
pdf(paste0(fig_dir, 'harmony_vlnplot_MG.pdf'), width=6, height=3, useDingbats=FALSE)
p
dev.off()



```

Test two different filtering options:
Filter doublets or filter based on UMIs:

```{r eval=FALSE}

#################################################################################
# Highlight potential doublets based on marker gene presence:
################################################################################

# how many cells are potential doublets?
potential_doublets <- c(18, 23, 26, 28, 30, 31, 35, 39)
table(seurat_obj@meta.data$leiden_res1.5 %in% potential_doublets)

p1 <- DimPlot(seurat_obj, reduction='paga_umap', cells.highlight=colnames(seurat_obj)[seurat_obj@meta.data$leiden_res1.5 %in% potential_doublets]) + umap_theme  + ggtitle('Potential Doublets') + theme(legend.position='bottom', plot.title = element_text(hjust = 0.5)) + NoLegend()

p2 <- FeaturePlot(seurat_obj, reduction='paga_umap', feature='nCount_RNA', order=TRUE)  +
    scale_color_gradientn(colors=rev(magma(256)), guide = guide_colorbar(barwidth=0.5, barheight=10, ticks=FALSE)) +
    umap_theme

pdf(paste0(fig_dir, 'umap_potential_doublets.pdf'), width=10, height=5)
p1 + p2
dev.off()


# plot UMAP with high quality cells only:

p3 <- DimPlot(seurat_obj, reduction='paga_umap', label=TRUE, cells.highlight=colnames(seurat_obj)[seurat_obj$nCount_RNA > 60000]) + NoLegend() + umap_theme + ggtitle('nCount_RNA > 60,000') + theme(legend.position='bottom', plot.title = element_text(hjust = 0.5)) + NoLegend()
pdf(paste0(fig_dir, 'umap_high_quality.pdf'), width=10, height=5)
p1 + p3
dev.off()

# how many cells would we get rid of?
potential_doublets <- c(18, 23, 26, 28, 30, 31, 35, 39)
table(seurat_obj@meta.data$leiden_res1.5 %in% potential_doublets)

table(seurat_obj$nCount_RNA >= 50000)


#################################################################################
# Highlight potential doublets based on marker gene presence:
################################################################################

# re-load seurat obj
seurat_obj <- readRDS(paste0(data_dir, 'FIRE_mouse_seurat.rds'))
scanpy_meta <- read.csv(paste0(data_dir,'scanpy_meta.csv'))
seurat_obj$leiden_res0.7 <- factor(scanpy_meta$leiden_res0.7, levels=min(scanpy_meta$leiden_res0.7):max(scanpy_meta$leiden_res0.7))
seurat_obj$leiden_res1.5 <- factor(scanpy_meta$leiden_res1.5, levels=min(scanpy_meta$leiden_res1.5):max(scanpy_meta$leiden_res1.5))
Idents(seurat_obj) <- seurat_obj$leiden_res1.5

paga_umap <- as.matrix(select(scanpy_meta, c(paga_UMAP1, paga_UMAP2)))
rownames(paga_umap) <- colnames(seurat_obj)
seurat_obj@reductions$paga_umap <-  CreateDimReducObject(
    embeddings=paga_umap,
    key="umap_",
    assay="RNA"
)

# filter (we are using the doublet filter)
potential_doublets <- c(18, 23, 26, 28, 30, 31, 35, 39)
filter <- !(seurat_obj@meta.data$leiden_res1.5 %in% potential_doublets); name <- 'doublet_filter'
# filter <- !(seurat_obj$nCount_RNA > 50000); name <- 'UMI_filter'
# filter <- !(seurat_obj$nCount_RNA > 50000 | seurat_obj@meta.data$leiden_res1.5 %in% potential_doublets); name <- 'both_filters'
# table(filter)

seurat_obj <- seurat_obj[,filter]


# processing:
seurat_obj <- FindVariableFeatures(seurat_obj, nfeatures=3500)
VariableFeatures(seurat_obj) <- VariableFeatures(seurat_obj)[!grepl("^mt-", VariableFeatures(seurat_obj))]
seurat_obj <- RunPCA(seurat_obj, features=VariableFeatures(seurat_obj))
seurat_obj <- RunHarmony(seurat_obj, dims=1:20, group.by='SampleID')
seurat_obj <- RunUMAP(seurat_obj, reduction='harmony', dims = 1:20, n.neighbors=15L, min.dist=0.10)
seurat_obj <- FindNeighbors(seurat_obj, dims=1:20, reduction='harmony', annoy.metric='cosine')
seurat_obj <- FindClusters(seurat_obj, resolution = 0.7)

# plot resulting UMAP:
p1 <- DimPlot(seurat_obj, group.by='seurat_clusters', label=TRUE) + umap_theme + NoLegend() + ggtitle('seurat clusters') + theme(plot.title = element_text(hjust = 0.5))
p2 <- DimPlot(seurat_obj, group.by='leiden_res1.5', label=TRUE) + umap_theme + NoLegend() + ggtitle('leiden clusters') + theme(plot.title = element_text(hjust = 0.5))

pdf(paste0(fig_dir, 'umap_', name, '_clusters.pdf'), width=10, height=5)
p1 + p2
dev.off()


# marker gene dortplot
markers <- c('Rgs5', 'Mybpc1', 'Dnah11', 'Slc47a1', 'Slc6a13','Csf1r', 'Cx3cr1', 'Cd163', 'Tnc', 'Gfap', 'Aqp4', 'Mobp', 'Mog', 'Pdgfra', 'Slc17a7', 'Rorb', 'Themis', 'Nrgn', 'Gad2', 'Vip', 'Pvalb', 'Sst', 'Lamp5')
p <- DotPlot(seurat_obj, features=markers) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256))) + ylab('') + xlab('')
pdf(paste0(fig_dir, 'dotplot_markers_', name, '.pdf'), width=12, height=6, useDingbats=FALSE)
p
dev.off()

pdf(paste0(fig_dir, 'umap_and_dotplot_markers_', name, '.pdf'), width=14, height=6, useDingbats=FALSE)
p1 + p
dev.off()



# save seurat object

saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat.rds'))

# save individual pieces of seurat object to load into python:

# save data matrix:
X <- GetAssayData(seurat_obj, assay='RNA', slot='data')
Matrix::writeMM(X, file=paste0(data_dir, 'FIRE_mouse_normCounts.mtx'))

# save gene names:
write.table(
  data.frame('gene'=rownames(X)),
  file=paste0(data_dir, 'gene_names.csv'),
  quote=F,
  row.names=F,
  col.names=F
)

# save harmony matrix as csv
write.csv(seurat_obj@reductions$harmony@cell.embeddings, file=, paste0(data_dir, 'FIRE_mouse_harmony.csv'), quote=F, row.names=F)

# save metadata:
meta <- seurat_obj@meta.data
meta$barcode <- colnames(seurat_obj)
meta$UMAP1 <- seurat_obj@reductions$umap@cell.embeddings[,1]
meta$UMAP2 <- seurat_obj@reductions$umap@cell.embeddings[,2]

write.csv(meta, file=paste0(data_dir, 'FIRE_mouse_meta.csv'), quote=F, row.names=F)


```



Transfer this scanpy data over to Seurat obj:
```{r eval=FALSE}

scanpy_meta <- read.csv(paste0(data_dir,'scanpy_meta.csv'))
seurat_obj$leiden_res0.7 <- factor(scanpy_meta$leiden_res0.7, levels=min(scanpy_meta$leiden_res0.7):max(scanpy_meta$leiden_res0.7))
seurat_obj$leiden_res1.5 <- factor(scanpy_meta$leiden_res1.5, levels=min(scanpy_meta$leiden_res1.5):max(scanpy_meta$leiden_res1.5))
Idents(seurat_obj) <- seurat_obj$leiden_res0.7

paga_umap <- as.matrix(select(scanpy_meta, c(paga_UMAP1, paga_UMAP2)))
rownames(paga_umap) <- colnames(seurat_obj)
seurat_obj@reductions$paga_umap <-  CreateDimReducObject(
    embeddings=paga_umap,
    key="umap_",
    assay="RNA"
)

# save seurat obj:
saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat.rds'))

# UMAP + Clusters
p <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap') + umap_theme
pdf(paste0(fig_dir, 'umap_clusters_final.pdf'), width=8, height=7)
p
dev.off()


```

























Cluster DEGS:
```{r eval=FALSE}

de_markers <- FindAllMarkers(
  seurat_obj,
  test.use = "MAST",
  only.pos = TRUE,
  min.pct = 0.25,
  logfc.threshold = 0.5
)
save(de_markers, paste0(data_dir, 'leiden1.5_markers.rda'))
saveRDS(seurat_obj, paste0(data_dir, 'FIRE_mouse_seurat.rds'))



# use presto for fast results:
library(presto)

presto_markers <- presto::wilcoxauc(seurat_obj, 'leiden_res1.5')
save(presto_markers, file=paste0(data_dir, 'presto_markers.rda'))


# how many cells are potential doublets?
potential_doublets <- c(18, 23, 26, 28, 30, 31, 35, 39)
seurat_obj$potential_doublets <-
table(seurat_obj@meta.data$leiden_res1.5 %in% potential_doublets)

```



<!--

Integrate conditions using Liger:
```{r eval=FALSE}

library(liger)

counts <- GetAssayData(seurat_obj, slot='counts')

counts_list <- list(
  '5x-Mut-CELL' = counts[,seurat_obj$DX == '5x-Mut-CELL'],
  '5x-Mut-NA' = counts[,seurat_obj$DX == '5x-Mut-NA'],
  '5x-Mut-PBS' = counts[,seurat_obj$DX == '5x-Mut-PBS'],
  '5x-Wt-NA' = counts[,seurat_obj$DX == '5x-Wt-NA'],
  'Wt-Mut-NA' = counts[,seurat_obj$DX == 'Wt-Mut-NA'],
  'Wt-Wt-NA' = counts[,seurat_obj$DX == 'Wt-Wt-NA']
)


a.NucSeq <- createLiger(counts_list)
a.NucSeq <- normalize(a.NucSeq)
pdf(paste0(fig_dir, "liger_variable_genes.pdf"), width=8, height=8)
a.NucSeq <- selectGenes(a.NucSeq, var.thresh =c(0.2, 0.1, 0.2, 0.125, 0.125, 0.2), do.plot=T)
dev.off()
a.NucSeq <- scaleNotCenter(a.NucSeq)

# perform online iNMF
a.NucSeq = online_iNMF(a.NucSeq, k = 30, max.epochs = 5)

# quantile normalization
a.NucSeq  = quantile_norm(a.NucSeq)
a.NucSeq  = runUMAP(a.NucSeq)

pdf(paste0(fig_dir, 'liger_umap.pdf'), width=8, height=8)
plotByDatasetAndCluster(a.NucSeq, axis.labels = c("UMAP1","UMAP2"))
dev.off()

pdf(paste0(fig_dir, 'liger_featureplot.pdf'), width=5, height=5)
plotGene(a.NucSeq, 'Mog', return.plots=F)
dev.off()

# transfer to seurat object:
seurat_obj@reductions$iNMF <-  CreateDimReducObject(
    loadings=t(a.NucSeq@W),
    embeddings=a.NucSeq@H.norm[colnames(seurat_obj),],
    key="iNMF_",
    assay="RNA"
  )
VariableFeatures(seurat_obj) <- a.NucSeq@var.genes

seurat_obj <- RunUMAP(seurat_obj, reduction='iNMF', dims = 1:30)
seurat_obj <- FindNeighbors(seurat_obj, reduction='iNMF')
seurat_obj <- FindClusters(seurat_obj, resolution = 0.75)


# UMAP + Clusters
p <- DimPlot(seurat_obj, label=TRUE) + umap_theme
pdf(paste0(fig_dir, 'umap_inmf_clusters.pdf'), width=8, height=7)
p
dev.off()

# color by sample
p <- DimPlot(seurat_obj, group.by='SampleID') + umap_theme
pdf(paste0(fig_dir, 'umap_inmf_samples.pdf'), width=10, height=7)
p
dev.off()

``` -->
