

After filtering low-quality cells and doublets, UMAP + clustering, we can
start annotating clusters based on cell-type identities.

* Investigate expression literature-curated cell-type marker genes
* quick and dirty DEG analysis using Presto
* Annotation based on above information
* Composition of major cell-types
  - sublibrary
  - sample
  - condition

After this, we can re-embed and sub-cluster each of the major types, and perform
a more thorough DEG analysis using MAST (separate notebook).

# Load data

```{r eval=FALSE}

library(Seurat)
library(tidyverse)
library(cowplot)
library(Matrix)
library(viridis)
library(presto)
library(harmony)
library(RColorBrewer)
library(patchwork)
library(ggpubr)
theme_set(theme_cowplot())

setwd("/dfs3b/swaruplab/smorabit/analysis/FIRE_mouse_2021/")

# directories
data_dir <- "data/"
fig_dir <- 'figures/'

umap_theme <- theme(
  axis.line=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks=element_blank(),
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  panel.background=element_blank(),
  panel.border=element_blank(),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  plot.background=element_blank()
)

# re-load data
seurat_obj <- readRDS(file=paste0(data_dir, 'FIRE_mouse_seurat.rds'))
setwd("/dfs3b/swaruplab/smorabit/analysis/FIRE_mouse_2021/composition")

# color scheme for samples:
color.scheme <- c(
  brewer.pal(9, 'Reds')[2:9],
  brewer.pal(9, 'Purples')[2:9],
  brewer.pal(9, 'Oranges')[2:9],
  brewer.pal(9, 'Greys')[2:9],
  brewer.pal(9, 'Blues')[2:9],
  brewer.pal(9, 'Greens')[2:9]
)
names(color.scheme) <- as.character(levels(seurat_obj$SampleID))

```

# Expression of literature-curated marker genes:

```{r eval=FALSE}

seurat_obj <- readRDS('EDA/data/FIRE_mouse_seurat.rds')

marker_list <- list(
  'EX' = c('Slc17a7', 'Lamp5', 'Rorb'),
  'INH' = c('Gad1', 'Gad2', 'Slc32a1', 'Vip', 'Sst', 'Pvalb'),
  'ASC' = c('Aqp4', 'Gfap', 'Slc7a10', 'Prdm16', 'Tnc'),
  'MG' = c('Csf1r', 'Cx3cr1'),
  'Mature-ODC' = c('Mog', 'Klk6', 'Mobp'),
  'Mf-ODC' = c('Opalin', 'Plp1', 'Cnp', 'Sox10'),
  'Nf-ODC' = c('Tcf7l2', 'Itpr2', 'Tmem2'),
  'COP' = c('Sox6', 'Nkx2-2', 'Bmp4', 'Vcan'),
  'OPC' = c('Pdgfra', 'Cspg4', 'Ptprz1'),
  'VLMC' = c('Vtn', 'Slc47a1', 'Slc6a13'),
  'OEC' = c('Mybpc1'),
  'END' = c('Rgs5'),
  'EPD' = c('Dnah11')
)



dir.create(paste0(fig_dir, 'literature_markers'))

# make a dot plot for all markers:
p <- DotPlot(seurat_obj, features=as.character(unlist(marker_list)), dot.min=0.1, group.by='clusternum_anno') + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256))) + ylab('') + xlab('')
pdf(paste0(fig_dir, 'literature_markers/all_clusters_markers_dotplot.pdf'), width=12, height=8, useDingbats=FALSE)
p
dev.off()

# violin plots for each of these markers:
for(i in 1:length(marker_list)){

  markers = as.character(unlist(marker_list[i]))
  name = names(marker_list)[i]
  print(name)

  # violin plot for these genes
  plot_list <- VlnPlot(seurat_obj, features=markers, pt.size=0, combine=FALSE)
  pdf(paste0(fig_dir, 'literature_markers/', name, '_markers_vlnplot.pdf'), width=7, height=2)
  for(p in plot_list){
    p <- p + xlab('') + ylab('') + NoLegend()
    print(p)
  }
  dev.off()

  # dot plot for these genes:
  p <- DotPlot(seurat_obj, features=markers) + coord_flip() + RotatedAxis() + scale_color_gradientn(colors=rev(viridis(256))) + ylab('') + xlab('')
  pdf(paste0(fig_dir, 'literature_markers/', name, '_markers_dotplot.pdf'), width=8, height=1.5 + (length(markers)*0.5), useDingbats=FALSE)
  print(p)
  dev.off()

}

```

# Annotations based on these markers:

```{r eval=FALSE}

annot_df <- data.frame(
  annotation = c(
    'INH',
    'EX',
    'INH',
    'EX',
    'ASC',
    'EX',
    'EX',
    'EX',
    'INH',
    'END',
    'INH',
    'ODC',
    'EX',
    'EX',
    'EX',
    'INH',
    'MG',
    'OPC',
    'EX',
    'VLMC',
    'Neuron (Doublet?)',
    'EPD',
    'EX',
    'EPD',
    'OEC',
    'Neuron (Doublet?)'
  ),
  clusters = 0:max(as.numeric(as.character(Idents(seurat_obj))))
)

seurat_obj$cluster_anno <- annot_df$annotation[match(as.numeric(as.character(Idents(seurat_obj))), annot_df$clusters)]
seurat_obj$cluster_anno <- factor(as.character(seurat_obj$cluster_anno), levels=unique(as.character(annot_df$annotation)))

# cluster number + annotation
seurat_obj$clusternum_anno <- paste0(as.numeric(as.character(seurat_obj$leiden_res0.7)), '-', as.character(seurat_obj$cluster_anno))

# plot UMAP
p <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap', group.by='clusternum_anno') + umap_theme
pdf(paste0(fig_dir, 'umap_clusters_annotated.pdf'), width=10, height=7)
p
dev.off()

# plot nUMI
p2 <- FeaturePlot(seurat_obj, reduction='paga_umap', feature='nCount_RNA', order=TRUE)  +
    scale_color_gradientn(colors=rev(magma(256)), guide = guide_colorbar(barwidth=0.5, barheight=10, ticks=FALSE)) +
    umap_theme

p3 <- VlnPlot(seurat_obj, features='nCount_RNA', group.by='clusternum_anno', pt.size=0) + xlab('') + ylab('') + NoLegend()

pdf(paste0(fig_dir, 'clusters_and_nUMI.pdf'), width=10, height=10)
patch <- (p + NoLegend() + ggtitle('annotated clusters') +  theme(plot.title = element_text(hjust = 0.5))) + p2
patch / p3 + plot_layout(heights=c(2,1))
dev.off()

#################################################################################
#  Remove potential doublet clusters 21 and 26:
################################################################################

seurat_obj <- seurat_obj[,!c(seurat_obj$leiden_res0.7 %in% c(20, 25))]


p <- DimPlot(seurat_obj, label=TRUE, reduction='paga_umap', group.by='clusternum_anno') + umap_theme
pdf(paste0(fig_dir, 'umap_clusters_annotated.pdf'), width=10, height=7)
p
dev.off()

celltype_color.scheme <- brewer.pal(10, 'Paired')
p <- DimPlot(seurat_obj, reduction='paga_umap', group.by='cluster_anno') + umap_theme +
  scale_color_manual(values=celltype_color.scheme)
pdf(paste0(fig_dir, 'umap_celltypes_annotated.pdf'), width=6, height=5)
p
dev.off()

# save seurat obj:
saveRDS(seurat_obj, file=paste0(data_dir, 'FIRE_mouse_seurat.rds'))

```

Expression of canonical marker genes in each major cell type
* Heatmap
* VlnPlot
* DotPlot

```{r eval=FALSE}

markers <- c('Slc17a7', 'Gad2', 'Aqp4', 'Rgs5', 'Mog', 'Csf1r', 'Pdgfra', 'Slc47a1', 'Dnah11', 'Mybpc1')

seurat_obj$cluster_anno <- factor(
  as.character(seurat_obj$cluster_anno),
  levels=c('EX', 'INH', 'ASC', 'END', 'ODC', 'MG', 'OPC', 'VLMC', 'EPD', 'OEC')
)

p <- DoHeatmap(seurat_obj, features=markers, group.by='cluster_anno', label=FALSE) +
  scale_fill_gradientn(colors=viridis(256))

pdf(paste0(fig_dir, 'heatmap_canonical_markers.pdf'), width=10, height=5)
p
dev.off()


```


Dataset composition by major cell types:

* How many cells of each cell type?
* How many cells in each sample? (Split by DX group)

```{r eval=FALSE}

# change the name of the different groups:
# seurat_obj$group <- seurat_obj$DX
# group_df <- data.frame(
#   'group' = c('WT', '5xFAD', 'FIRE', '5xFIRE', '5xFIRE + PBS', '5xFIRE + transplant'),
#   'DX' = c('Wt-Wt-NA', '5x-Wt-NA', 'Wt-Mut-NA', '5x-Mut-NA', '5x-Mut-PBS', '5x-Mut-CELL'),
#   stringsAsFactors=FALSE
# )
#
# seurat_obj$DX <- factor(
#   group_df$group[match(as.character(seurat_obj$group), as.character(group_df$DX))],
#   levels = c('WT', '5xFAD', 'FIRE', '5xFIRE', '5xFIRE + PBS', '5xFIRE + transplant')
# )

#################################################################################
# number of cells of each major cell type:
#################################################################################

df <- as.data.frame(table(droplevels(seurat_obj$class)))

p <- ggplot(df, aes(x=reorder(Var1, -Freq), y=Freq, fill=Var1)) +
  geom_bar(stat='identity') + NoLegend() + RotatedAxis() + ylab(expression(italic(N)[cells])) + xlab('') +
  geom_text(aes(label=scales::comma(Freq)),  color="black", size=3.5) +
  scale_y_continuous(labels=scales::comma) +
  ggtitle(paste('Total number of cells post-filtering:', scales::comma(ncol(seurat_obj)))) +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.y=element_line(colour="lightgray", size=0.5),
    axis.ticks.x=element_blank(),
  )

pdf(paste0(fig_dir, 'barplot_nCells_celltypes.pdf'), width=6, height=3)
p
dev.off()

#################################################################################
# number of cells of each cluster
#################################################################################

df <- as.data.frame(table((seurat_obj$clusternum_anno)))

p <- ggplot(df, aes(x=reorder(Var1, Freq), y=Freq, fill=Var1)) +
  geom_bar(stat='identity') + NoLegend() + RotatedAxis() + ylab(expression(italic(N)[cells])) + xlab('') +
  geom_text(aes(label=scales::comma(Freq)),  color="black", size=3.5, hjust='inward') +
  scale_y_continuous(labels=scales::comma) +
  coord_flip() +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.ticks.x=element_blank(),
  )

pdf(paste0(fig_dir, 'barplot_nCells_clusters.pdf'), width=4, height=8)
p
dev.off()


#################################################################################
# number of cells in each sample:
#################################################################################

df <- as.data.frame(table(seurat_obj$SampleID))
df$group <- factor(
  as.character(seurat_obj@meta.data$DX)[match(as.character(df$Var1), seurat_obj@meta.data$SampleID)],
  levels = levels(seurat_obj$DX)
)

p <- ggplot(df, aes(x=reorder(Var1, Freq), y=Freq, fill=Var1, )) +
  geom_bar(stat='identity') +
  geom_text(aes(label=scales::comma(Freq)),  color="black", size=3.5, hjust='inward') +
  scale_y_continuous(labels=scales::comma) +
  scale_fill_manual(values=color.scheme) +
  coord_flip() + NoLegend() + RotatedAxis() + xlab('') +  ylab(expression(italic(N)[cells])) +
  ggtitle('Number of cells per sample in each condition') + theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.x=element_line(colour="lightgray", size=0.5),
    axis.ticks.y=element_blank(),
  )

pdf(paste0(fig_dir, 'barplot_nCells_samples.pdf'), width=7, height=6)
p + facet_wrap(~group, scales='free_y', ncol=3)
dev.off()

# umap colored by sample:
p <- DimPlot(seurat_obj, split.by='DX', group.by='SampleID', ncol=3, reduction='paga_umap') +
  umap_theme + scale_color_manual(values=color.scheme)
pdf(paste0(fig_dir, 'umap_sample_splitby_DX.pdf'), width=10, height=6)
p
dev.off()



#################################################################################
# number of cells in each sublibrary
#################################################################################

df <- as.data.frame(table((seurat_obj$sublibrary)))

p <- ggplot(df, aes(x=reorder(Var1, -Freq), y=Freq, fill=Var1)) +
  geom_bar(stat='identity') + NoLegend() + RotatedAxis() + ylab(expression(italic(N)[cells])) + xlab('') +
  scale_y_continuous(labels=scales::comma) +
  geom_text(aes(label=scales::comma(Freq)),  color="black", size=3.5) +
  ggtitle('Number of cells per sublibrary') +
  theme(
    plot.title = element_text(hjust = 0.5),
    panel.grid.minor=element_blank(),
    panel.grid.major.y=element_line(colour="lightgray", size=0.5),
    axis.ticks.x=element_blank(),
  )

pdf(paste0(fig_dir, 'barplot_nCells_sublibrary.pdf'), width=6, height=3)
p
dev.off()

# umap colored by sublibrary
p <- DimPlot(seurat_obj,  group.by='sublibrary', reduction='paga_umap') +
  umap_theme
pdf(paste0(fig_dir, 'umap_sublibrary.pdf'), width=7, height=6)
p
dev.off()

# umap colored by sublibrary
p <- DimPlot(seurat_obj, split.by='sublibrary', group.by='sublibrary', reduction='paga_umap', ncol=4) +
  umap_theme + NoLegend()
pdf(paste0(fig_dir, 'umap_sublibrary_split.pdf'), width=12, height=6)
p
dev.off()

#################################################################################
# Proportion of major cell types
#################################################################################

seurat_meta <- seurat_obj@meta.data %>% subset(class %in% c('INH', 'EX')); name='neuronal'; w=6;h=10;
seurat_meta <- seurat_obj@meta.data %>% subset(!class %in% c('INH', 'EX')); name='non-neuronal'; w=6;h=10;

#seurat_meta$cluster_anno <- droplevels(seurat_meta$cluster_anno)

meta_list <- seurat_meta%>%
  dplyr::group_split(SampleID)

temp <- lapply(meta_list, function(meta){
  df <- as.data.frame(meta$clusternum_anno %>% table / nrow(meta))
  colnames(df) <- c('cluster', 'proportion')
  df$SampleID <- unique(meta$SampleID)
  df$DX <- unique(meta$DX)
  df
})

proportion_df <- Reduce(rbind, temp)
proportion_df$cluster_num <- as.numeric(proportion_df$cluster)

#
#
# sample_color.scheme <- c(
#   brewer.pal(9, 'Greys')[5],
#   brewer.pal(9, 'Purples')[7],
#   brewer.pal(9, 'Oranges')[6],
#   brewer.pal(9, 'Reds')[6],
#   brewer.pal(9, 'Blues')[5],
#   brewer.pal(9, 'Greens')[5]
# )
# names(sample_color.scheme) <- levels(seurat_obj$DX)
#
#
# # set up comparison lists:
comparisons <- list(c(2,1), c(5,3),  c(3,1), c(5,1))


pdf(paste0(fig_dir, name,'_composition_boxplot.pdf'), width=5, height=3)
plot_list <- list()
for(cl in unique(proportion_df$cluster)){
  cur_df <- subset(proportion_df, cluster==cl)
  #m_df <- cur_df %>% group_by(DX) %>% summarize(median = mean(proportion))


  p <- ggplot(cur_df, aes(y=proportion, x=reorder(DX, DX), fill=DX)) +
    scale_x_discrete(limits=rev(levels(cur_df$DX))) +
    #geom_bar(aes.inherit=FALSE, data=m_df, aes(y=median, x=DX, fill=DX), alpha=0.5, stat='identity') +
    geom_boxplot(outlier.shape=NA, color='black', alpha=0.7) +
    geom_jitter(aes(color=SampleID), size=1.5, width=0.25) +
    scale_fill_manual(values=sample_color.scheme) +
    scale_color_manual(values=color.scheme) +
    ggtitle(cl) +
    coord_flip() +
    labs(fill='') + NoLegend() +
    stat_compare_means(method='wilcox', comparisons=comparisons, label='p.signif') +
    # scale_x_discrete(limits = rev(levels(cluster))) +
    theme(
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x=element_line(colour="lightgray", size=0.5),
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank()
    ) + xlab('') + ylab(paste('proportion', name))

  print(p)
  plot_list[[cl]] <- p
}
dev.off()



# neuronal
pdf(paste0(fig_dir, name,'_composition_boxplot_combined.pdf'), width=20, height=16)
wrap_plots(plot_list, ncol=5)
dev.off()

# non-neuronal
pdf(paste0(fig_dir, name,'_composition_boxplot_combined.pdf'), width=12, height=9)
wrap_plots(plot_list, ncol=3)
dev.off()


```
